Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-26 Latex/journal_v1/V4/pr.tex
add latex

In addition, $T_{RU}^{u(s,i)}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
 The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
an exponential distribution with mean $1/(R_{u(s,i)}$ and can be modeled as a M/M/1 queue.

@@

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\

@@

&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\

@@

\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (1 + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0

@@

p_{r,u(s,i)}^{k} = [\frac{(1 + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.

@@

\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})\\

@@

Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(1+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
Next we introduce the  method which is a greedy algorithm.

\textit{Greedy Algorithm:}

@@

\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}  g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\

@@

The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  

@@

Then we define ${RU}_{resid} = \mathcal{R} $ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
as a set of O-RUs and value of each O-RU, respectively.
Afterward, we assign the O-RU that provides the highest achievable rate for each UE on the condition that 

@@

Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$ 
The complexity of this algorithm is about $O(N\times \mathfrak{N})$

@@

\State Set ${RU}_{resid} = \mathcal{R} $ and $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}

@@

@@

\State Acquire $\mathfrak{G}_r = \bar{\mathcal{R}}^r_{u_{(s,k)}}$

@@

\State Obtain $r = \text{argmax}_r \mathfrak{G}_r$
\While{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\If{$\mathfrak{C}_r \geq \psi_{r,u(s,i)}$}
\State Set $g^r_{u(s,i)} = 1$ and $\mathfrak{C}_r = \mathfrak{C}_r - \psi_{r,u(s,i)}$

@@

\State  ${RU}_{resid} = \mathcal{R} \setminus \{r\} $

@@

>>>>

In addition, $T_{RU}^{u(s,i)}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
 The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue.

@@

Suppose each slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\

@@

&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\

@@

\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} = (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k} + (\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k})=0

@@

p_{r,u(s,i)}^{k} = [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{\kappa^k_{r,u(s,i)} -\mathfrak{m}_{r}\mathfrak{D}_{r,u(s,i)}^{k}} -\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.

@@

\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\

@@

Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
Next we introduce two methods which are both greedy algorithm.
The first method is a greedy algorithm that assign one O-RU to each UE and the second method is
a greedy algorithm that assign one or more than one O-RU to each UE and use coordinated multipoint (CoMP) transmissions \cite{yang2021multicast}.
\begin{enumerate}
\item\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}

@@

\max\limits_{ \boldsymbol{G} }   \quad &  \sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R} \delta_s g^r_{u(s,i)}\bar{\mathcal{R}}^r_{u_{(s,k)}} \ \\

@@

& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\

@@

The problem \eqref{problem2} is an integer linear programming.
By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
the problem \eqref{problem2} becomes to an NP-complete 0-1 multiple knapsack problem.  

@@

Then we define ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$ and $ \mathfrak{C}_r = \mathfrak{t}_r, \forall r$
as a set of all O-RUs and value of each O-RU, respectively.
Next, we sort all slices based on their priority. 
Afterward, we assign the O-RU that provides the highest achievable rate for each UE (we start from the UEs on the slices with highest priority) on the condition that 

@@

The complexity of sorting S slices based on their priority is $O(Slog(S))$.
Depict $\mathfrak{N} =  \sum_{s=1}^S\sum_{i=1}^{U_s} 1$. 
The complexity of this algorithm is about $O(Slog(s)) + O(R\times \mathfrak{N})$.
%$O(N\times \mathfrak{N})$

@@

\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
\State Sort slices according to their priority factor ($\delta_s$) in descending order

@@

\State $RU = 0$

@@

\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$

@@

\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\While{$RU == 0$}
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
\State Set $g^{r^*}_{u(s,i)} = 1$ 
\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
\State Set $RU = 1$ 

@@

\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $

@@

\item\textit{Greedy Algorithm for Comp O-RU Assignment:}
Here we want to solve problem \eqref{problem2}, by assuming that one or more than one O-RU can assign to each UE.
We solve this problem using GACA algorithm which used GAAOU algorithm.
In this algorithm, Firstly we sort slices based on their priority (So the UEs of slices are sorted too).
Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{32}
\State Set $\mathtt{R}^{t} = 0$
\State Sort slices according to their priority factor ($\delta_s$) in descending order
\State $RU = 0$
\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\While{$RU == 0$}
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
\State Set $g^{r^*}_{u(s,i)} = 1$ 
\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\For {$s \gets 1$ to $S$}
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$} 
\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\State $g^{r^*}_{u(s,i)} = 1$ 
\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
\State Set $g^{r^*}_{u(s,i)} = 0$
\State update $\mathtt{R}^{t}$
\end{enumerate}
